Placeholder

### 2021-02-08 Paper_Histograms.Rmd
Removed plot style 2 for the retro diagnosis graph

#Graph 2
retro_ethnicity_non_white <- dat.retro_ethnicity_non_white %>% 
  ggplot(aes(x = Ethnicity_collapsed, y = n, fill = Sample_plot)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "",
       x = "Ethnic origin",
       y = "N participants") +
  scale_x_discrete(guide = guide_axis(n.dodge = 3)) +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank()) +
  geom_text(aes(label = n),
            size = 3,
            position = position_dodge(width=0.9), 
            vjust=-0.25)

@@

#####Plot Style 2

dat.retro_positive_diagnosis_by_sample %>% 
  ggplot(aes(x = reorder(Diagnosis, -positive_n), y = positive_n, fill = Sample_plot)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "",
       y = "") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  theme(legend.position = "top") + 
  theme(legend.title = element_blank()) +
  ylim(0, 20000)

>>>>

#Graph 2
retro_ethnicity_non_white <- dat.retro_ethnicity_non_white %>% 
  ggplot(aes(x = Ethnicity_collapsed, y = n, fill = Sample_plot)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "",
       x = "Ethnic origin",
       y = "N participants") +
theme(axis.text.x = element_text(angle = 70, vjust = 0.5)) +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank()) +
  geom_text(aes(label = n),
            size = 2,
            position = position_dodge(width=0.9), 
            vjust=-0.25)

@@
